\textit{Supplementary materials for}: Text embedding models yield high resolution insights into conceptual knowledge from short multiple choice quizzes

### 2023-02-01 paper/supplement.tex

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{figs/topic-weights}

\caption{\textbf{Averarge topic weights for each lecture and question type}.
The bar plots display the variance of each topic's weight across lecture
timepoints (top row) and questions (bottom row); colors denote topics. The
top-weighted words from the most heavily weighted topics are displayed in the
upper right (orange: topic 2; yellow-green: topic 4). The top-weighted words
from the full set of topics may be found in Table~S2. Also see
Figure~\topics A in the main text.}

>>>>

\begin{figure}[tp]
    \includegraphics[width=\textwidth]{figs/topic-weights}

\caption{\textbf{Topic weights. A. Average topic weights for each lecture and
question type}. The bar plots display each topic's average weight across
lecture timepoints (top row) and questions (bottom row); colors denote topics.
The top-weighted words from the highest-weighted topic from each lecture are
displayed in the upper right (orange: topic 2; yellow-green: topic 4). The
top-weighted words from the full set of topics may be found in
Table~\ref{tab:topics}. \textbf{B. Relationships between average topic
weights.} Pairwise correlations between the distributions of average topic
weights for each lecture and question category. Each row and column corresponds
to a bar plot in Panel A. Also see Figure~\topics A in the main text.}
